VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_eval.tex
centering table
re

{\bf Settings}.
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data and each 1TB data represents one snapshot version
of 25 VMs.  The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

The space cost for each snapshot deletion is insignificant.
Leakage repair for each VM needs less than 85MB of memory
considering each reference consumes 8 bytes plus  1 mark bit and  
each VM snapshot has 40GB backup data with about 10 million chunks. 
This VM-specific leakage  repair takes  less than half an hour for each VM, 
when disk bandwidth is controlled to 50MB/s. 
%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
%a total of 212GB memory
%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
%To control the garbage growth, such a process needs to be conducted much more frequently than our
%VM-centric leakage repair.

>>>>

{\bf Settings}.
We have performed a trace-driven study based on a production dataset
from Alibaba Aliyun's cloud platform~\cite{Aliyun} 
with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data and each 1TB data represents one snapshot version
of 25 VMs.  The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

The space cost for each snapshot deletion is insignificant.
Leakage repair for each VM needs less than 85MB of memory
considering each reference consumes 8 bytes plus  1 mark bit and  
each VM snapshot has 40GB backup data with about 10 million chunks. 
This VM-specific leakage  repair takes  less than half an hour for each VM. 
%when disk bandwidth is controlled to 50MB/s. 
%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
%a total of 212GB memory
%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
%To control the garbage growth, such a process needs to be conducted much more frequently than our
%VM-centric leakage repair.
